{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-10-31 main.tex
Add_Intro

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Function Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is getting more attention as researchers from different fields collect more data from a continuous underlying process. This data still can be processed by classical statistical methods, but only FDA allows answering questions that are tied to the information given by the smoothness of the underlying continuous process. (cf. \cite{levitin_introduction_2007})\\
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view one or more of the variables or units of a given data set as a smooth curve or function and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).
	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of a continuous underlying process. In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).

>>>>

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is getting more attention as researchers from different fields collect more data from a continuous underlying process. This data still can be processed by classical statistical methods, but only FDA allows answering questions that are tied to the information given by the smoothness of the underlying continuous process (cf. \cite{levitin_introduction_2007}).\\
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view one or more of the variables or units of a given data set as a smooth curve or function and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).
	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of a continuous underlying process. In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
	 The focus of this paper is to introduce Functional Linear Regression (FLR) in terms of scalar-on-function. We will be importing the standard FLR model, which shows functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}
	 $$Y_{i} = \beta_{0} + \int{X_{i}(s)\beta(s)ds} + \epsilon_{i},
	 \qquad i = 1, ..., n,$$
	 where $\{(X_{1}, Y_{1}), …, (X_{n}, Y_{n})\}$ is the realization of data, where $X_{i}$’s are independent and identically distributed random function X and $\beta(s)$ is the coefficient function. The distinct is that the estimator is not a scalar but a function, which leads to compelling interest in $\beta(s)$ for prediction. The information about the function comes up with how large or small a future observation $x$ of $X$ will influence the response with the leverage on $\int{\beta(s)xds}$. For instance, fluctuation in $X$ does not have any effect on $Y$, where $\beta(s)$ = 0, or has a greater effect on $Y$ with larger $\beta(s)$. Additionally, assume that $\beta(s)$ is exactly a linear function for any interval. The effect of X is, then, constant on that interval.\\
	 Estimation of $\beta(s)$ is inherent in a problem of infinite dimension. In Section 2, after constructing necessary theoretical properties to understand FDA, we progress to reduce dimension by utilizing smoothing with two types of basis function, namely, b-spline and eigenfunction. The results of the Monte-Carlo simulation regarding three different situations are reported in Section 3. Finally, in Section 4, we test the prediction of FLR with the actual data set. {\color{red} (We may put some simple descriptions of results about each of MC and Application)}
